Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-31 paper/paper.tex
20000 -> 20k

On the one hand, most publications in music information retrieval cast timbre modeling as an audio classification problem  \cite{martin1998asa,brown1999jasa,eronen2000icassp,herrera2003jnmr,wieczorkowska2003jiis,livshin2004dafx,krishna2004icassp,kaminskyj2005jiis,benetos2006icassp,bhalke2016jiis}.
In this context, the instrumentation of each musical excerpt serves as an unstructured set of ``audio tags,'' encoded as binary outputs within some predefined label space.
Because such tags often belong to the metadata of music releases, the process of curating a training set for musical instrument classification requires little or no human intervention.
Although scraping user-generated content from online music hosting platforms may not always reflect the true instrumentation with perfect accuracy, it offers a scalable and ecologically valid insight onto the acoustic underpinnings of musical timbre.
Furthermore, supplementing user-generated content with the outcome of a crowdsourced annotation campaign allows an explicit verification of instrument tags.
For instance, the Open-MIC dataset \cite{humphrey2018ismir}, maintained by the Community for Open and Sustainable Music Information Research (COSMIR) \cite{mcfee2016ismir}, comprises a vast corpus of 20000 polyphonic music recordings spanning 20 instruments as a derivative of the Free Music Archive (FMA) dataset \cite{defferrard2017ismir}.
Another example is the Medley-solos-DB dataset \cite{lostanlen2016ismir}, which comprises 21k monophonic excerpts from 8 instruments as a derivative of the MedleyDB dataset of multitrack music \cite{bittner2014ismir}.
Over the past decade, the availability of large digital audio collections, together with the democratization of high-performance computing on dedicated hardware, has spurred the development of deep learning architectures, and notably deep convolutional networks, in music instrument recognition \cite{mcfee2015ismir,pons2017eusipco,gururani2018ismir}.
Notwithstanding the growing accuracy of these architectures in the large data regime, it remains unclear how to extend them from musical instrument recognition to playing technique recognition, where labeled samples are considerably scarcer.
We refer to \cite{han2017taslp} for a recent review of the state of the art in this domain.

@@

The definition of the scattering transform in terms of wavelet decompositions and modulus nonlinearities presents several advantages.
On the computational side, the critical bandwidth guarantees of wavelet transforms allows us to judiciously subsample the output, resulting in a lower-dimensional representation compared to the cortical representations.
The scattering transform also satisfies the aforementioned stability conditions, providing a guarantee that slightly deforming a signal only results in a negligible change in its scattering transform.
Furthermore, we may calculate the scattering transforms of several model signals, including amplitude-modulated harmonic sounds and noise excitations \cite{anden2012scattering,anden2014tsp}, frequency-modulated sinusoids (e.g., chirps) \cite{anden2012scattering,anden2019tsp}, and beating phenomena \cite{anden2014tsp}.
They have also enjoyed success in several audio classification and similarity retrieval tasks \cite{anden2011multiscale,bauge2013representing,anden2014tsp,anden2019tsp,lostanlen2018jasmp,lostanlen2018extended}.
\ja{Need to flesh out the above with some equations.
We're no longer talking to biologists, so we don't need to be afraid.}%

>>>>

On the one hand, most publications in music information retrieval cast timbre modeling as an audio classification problem  \cite{martin1998asa,brown1999jasa,eronen2000icassp,herrera2003jnmr,wieczorkowska2003jiis,livshin2004dafx,krishna2004icassp,kaminskyj2005jiis,benetos2006icassp,bhalke2016jiis}.
In this context, the instrumentation of each musical excerpt serves as an unstructured set of ``audio tags,'' encoded as binary outputs within some predefined label space.
Because such tags often belong to the metadata of music releases, the process of curating a training set for musical instrument classification requires little or no human intervention.
Although scraping user-generated content from online music hosting platforms may not always reflect the true instrumentation with perfect accuracy, it offers a scalable and ecologically valid insight onto the acoustic underpinnings of musical timbre.
Furthermore, supplementing user-generated content with the outcome of a crowdsourced annotation campaign allows an explicit verification of instrument tags.
For instance, the Open-MIC dataset \cite{humphrey2018ismir}, maintained by the Community for Open and Sustainable Music Information Research (COSMIR) \cite{mcfee2016ismir}, comprises a vast corpus of 20k polyphonic music recordings spanning 20 instruments as a derivative of the Free Music Archive (FMA) dataset \cite{defferrard2017ismir}.
Another example is the Medley-solos-DB dataset \cite{lostanlen2016ismir}, which comprises 21k monophonic excerpts from 8 instruments as a derivative of the MedleyDB dataset of multitrack music \cite{bittner2014ismir}.
Over the past decade, the availability of large digital audio collections, together with the democratization of high-performance computing on dedicated hardware, has spurred the development of deep learning architectures, and notably deep convolutional networks, in music instrument recognition \cite{mcfee2015ismir,pons2017eusipco,gururani2018ismir}.
Notwithstanding the growing accuracy of these architectures in the large data regime, it remains unclear how to extend them from musical instrument recognition to playing technique recognition, where labeled samples are considerably scarcer.
We refer to \cite{han2017taslp} for a recent review of the state of the art in this domain.

@@

The definition of the scattering transform in terms of wavelet decompositions and modulus nonlinearities presents several advantages.
On the computational side, the critical bandwidth guarantees of wavelet transforms allows us to judiciously subsample the output, resulting in a lower-dimensional representation compared to the cortical representations.
The scattering transform also satisfies the aforementioned stability conditions, providing a guarantee that slightly deforming a signal only results in a negligible change in its scattering transform.
Furthermore, we may calculate the scattering transforms of several model signals, including amplitude-modulated harmonic sounds and noise excitations \cite{anden2012scattering,anden2014tsp}, frequency-modulated sinusoids (e.g., chirps) \cite{anden2012scattering,anden2019tsp}, and beating phenomena \cite{anden2014tsp}.
They have also enjoyed success in several audio classification and similarity retrieval tasks \cite{anden2011multiscale,bauge2013representing,anden2014tsp,anden2019tsp,lostanlen2018jasmp,lostanlen2018extended}.
%\ja{Need to flesh out the above with some equations.
%We're no longer talking to biologists, so we don't need to be afraid.}% i think we will put equations later, in the methods section, while making sure to re-use the notations lambda, alpha, beta. OK?
